\newpage
\chapter*{Preface}
% Here you can describe the process that led to the writing of this report (i.e., the project work process). Here you can mention why you chose this assignment and specific challenges you met with during your work. You can also thank people for help and support during this project.
%% Answer the following questions
%Have you done anything that doesn't have to do with your research?
%\\ Have you published parts of this work before?

%%% ACKNOWLEDGEMENT %%%
%Who is your advisor?
%\\
%Did anyone help you?
%\\
%Who funded this work?
%\\
%What's the name of your favourite pet?



This thesis is submitted to the department of Electronics Systems at NTNU as part of the Master of Science degree in Electronics, with specialization in digital circuit design. The project was proposed by the company Disruptive Technologies, and assigned to the author after discussions in May. The project was started on in the end of August 2017. 
\\

The purpose of this assignment is to evaluate different solutions for miniature camera systems, and estimate power dissipation and energy consumption. The assignment is quite broad, and gives the designer a large degree of freedom, which is both rewarding and demanding. 
\\

I would like to thank my supervisors; Håvard Tørring and Professor Snorre Aunet for guidance and help throughout the semester. A special thanks to Disruptive Technologies for providing the funds necessary to buy development kits and other equipment used in this project. I would also like to specially thank Postdoctoral Fellow Milica Orlandic for helping me with image compression for FPGAs, and for giving me an Intellectual Property for Sobel Edge detection, and for providing me with a testbench to test the design. \\

It is assumed that the reader has some basic knowledge in electronics and digital circuits.